---
title: "exam"
author: 'Lizzie (PID: 59010743)'
date: "5/29/2022"
output: pdf_document
---
**Load necessary packages. They were already installed using install.packages("package_name")**
```{r}
library(ggplot2)
library(lubridate)
library(dplyr)
```

**Import the data**
```{r}
dat <- read.csv("covid19_variants.csv")
```

**Look at the data**
```{r}
head(dat)
```

**Use lubridate to format the date column as actual dates and not a string**
```{r}
dat$date <- ymd(dat$date)
```

**Filter out the "Other" and "Total" entries**
```{r}
filter_dat <- filter(dat, variant_name != "Total" & variant_name != "Other")
```


**Plot the filtered data using ggplot. The x-axis is date in lubridate formate and y-axis is percentage. Geom_line allows for a line pot that can be colored by the variant. Labs enables labeling of axes and removal of label above variants by setting color="". scale_x_date allows you to set the x-axis tick marks, spacing by one month intervals, and labeling by abbreviated month name and year. lastly, we can apply the black and white theme and adjust the axis labels.**

```{r}
vid_plot <- ggplot(filter_dat) + aes(date, percentage) +
  geom_line(aes(color = variant_name)) +
  labs(x="", y="Percentage of sequenced specimens", 
       title= "Covid-19 Variants in California", color="") + 
  scale_x_date(date_breaks="1 month", date_labels="%b %Y") 
  
vid_plot + theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

