---
title: "Exam"
author: 'Lizzie West (PID: 59010743)'
date: "5/29/2022"
output:
  pdf_document: default
  word_document: default
---
# Steps
1. Make sure necessary packages are installed
2. Load necessary packages
3. Assign data to variable and look at data
4. Format dates using lubridate
5. Filter out entries that you do not want plotted
6. Generate plot using ggplot

**Load Packages**
```{r}
#Load necessary packages.They were already installed using install.packages("package_name")
library(ggplot2)
library(lubridate)
library(dplyr)
```

**Import Data**
```{r}
#Import the data
dat <- read.csv("covid19_variants.csv")
```

**Look at Data**
```{r}
#Look at the data
head(dat)
```

**Format Dates**
```{r}
#Use lubridate to format the date column as actual dates and not a string
dat$date <- ymd(dat$date)
```

**Filter Entries**
```{r}
#Filter out the "Other" and "Total" entries
filter_dat <- filter(dat, variant_name != "Total" & variant_name != "Other")
```


**Plot**

Plot the filtered data using ggplot. The x-axis is date in lubridate format
and y-axis is percentage. Geom_line allows for a line plot that can be colored 
by the variant. Labs enables labeling of axes and removal of label above variants by setting color="". scale_x_date allows you to set the x-axis tick marks, spacing by one month intervals, and labeling by abbreviated month name 
and year. Lastly, we can apply the black and white theme and adjust the axis labels.
```{r}
#Plot!
vid_plot <- ggplot(filter_dat) + aes(date, percentage) +
  geom_line(aes(color = variant_name)) +
  labs(x="", y="Percentage of sequenced specimens", 
       title= "Covid-19 Variants in California", color="") + 
  scale_x_date(date_breaks="1 month", date_labels="%b %Y") 
  
vid_plot + theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

